An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
section 5.5 pass plus other edits

\subsection{Applying the embedding framework}
When using our framework to study the consistency or inconsistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To do so, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
Second, identify the vertices of these polyhedral regions.%
\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates in \S~\ref{sec:top-k} which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
From here one can further remove redundant reports until arriving at a tight embedding if desired, or re-label embedded reports to a more intuitive form; call this resulting embedded loss $\hat \ell$.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$ from multiclass classification with an abtain option \S~\ref{sec:abstain} is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.

To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

The authors show that actually determining a calibrated link function in this case is nontrivial.
Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
Instead, \citeauthor{ourlovaszpaper} leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.

@@

%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ gives a set of label distribution $\P \subseteq \simplex$ such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
See Figure~\ref{fig:ordered-partition} for an illustration.
% gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ellOP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ellOP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ellOP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ellOP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ellOP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
% To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

\begin{figure}[H]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ellOP}$ (solid lines)
			%the property elicited by the ordered partition loss and embedded by $\LWW$, 
			juxtaposed against the level sets of $\mode$ (dashed lines).
%		The level sets of the mode (for which $\LWW$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ellOP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
      These offending cells correspond to reports whose highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

\subsection{Surrogates for top-$k$ classification}
\label{sec:top-k}
% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
% % for surrogate regret to approach target regret
% ~\citep{frongillo2021surrogate}.\jessiet{right?}
% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of $k$ labels, and given the true label $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
They further suggest that perhaps no surrogate could satisfy all three properties.
%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense! \#burn}}

@@

\citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
%\raft{Couldn't follow this sentence (commented out)}
% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.  better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.  Sentence commented out below could be useful in the caption.}
% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf. $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report less than $k$ labels.
The data distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.

@@

For example, consider one of the surrogates, $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$ and $n$ is the total number of labels;
the authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, \citeauthor{finocchiaro2022consistenttopk} go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.

Beyond analyzing the previously proposed surrogates, \citeauthor{finocchiaro2022consistenttopk} also use our framework to derive the first consistent polyhedral surrogate for $\elltopk$,
\begin{align}\label{eq:topk-embedding}
L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, n\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
\end{align}
That is, they show that indeed a surrogate exists satisfying convexity, consistency, and hinge-like structure.
In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.
This new surrogate $L^k$ is given directly by the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} and applying Theorem~\ref{thm:link-main} to obtain consistency.
While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is calibrated.
They indeed confirm its consistency using our framework, showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
% confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.

>>>>

\subsection{Applying the embedding framework}
\label{sec:apply-embedd-fram}

When using our framework to study the consistency or inconsistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To do so, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
Second, identify the vertices of these polyhedral regions.%
\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates in \S~\ref{sec:top-k} which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
From here one can further remove redundant reports until arriving at a tight embedding if desired, or re-label embedded reports to a more intuitive form; call this resulting embedded loss $\hat \ell$.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (in which case $\ell^f$ is a weighted Hamming loss).
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
The inclusion of abstain options is natural when observing that the BEP surrogate $\BEP$, for multiclass classification with an abtain option (\S~\ref{sec:abstain}), is the special case of $L^f$ where $f(S) = \ones\{S \neq \emptyset\}$.

To derive the discrete loss $\ellabs$ that $L^f$ embeds, the authors follow an approach similar to \S~\ref{sec:apply-embedd-fram} to show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, for any choice of $f$.
From Proposition~\ref{prop:representative-embeds-restriction}, they conclude that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
By Theorem~\ref{thm:link-main}, then, there is a link function such that the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

As \citeauthor{ourlovaszpaper} observe, actually determining a calibrated link function in this case is nontrivial.
Simple threshold links like for the BEP surrogate in \S~\ref{sec:abstain} are not always calibrated, thus casting doubt that a trial-and-error approach for finding the link would be successful.
Instead, the authors leverage our thickened link construction (Construction~\ref{const:eps-thick-link}) to derive two links $\psi^*$ and $\psi^\diamond$, which have somewhat intricate geometric structure (Figure~\ref{fig:lovasz-links}).
Perhaps surprisingly, by deriving the link envelope $\Psi$ which is contained in the envelopes for $L^f$ for all submodular and increasing $f$, they prove that $\psi^*(u) \subseteq \Psi(u)$ and $\psi^\diamond(u) \subseteq \Psi(u)$ for all $u \in \reals^d$.
Thus, both $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are simultaneously calibrated with respect to $\ellabs$ for all such $f$.

@@

%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $\LWW$ embeds $\ellOP$, \citeauthor{wang2020weston} then characterize $\prop{\ellOP}$.
In the same manner as Figure~\ref{fig:abstain-intuition-inconsistent}, knowledge of the level sets of $\prop{\ellOP}$ clarifies which label distributions are the source of inconsistency for classification.
Removing these distributions gives a set $\P \subseteq \simplex$
such that $\LWW$ and the canonical link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., such that eq.~\eqref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ellOP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
See Figure~\ref{fig:ordered-partition} for an illustration.
% gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ellOP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ellOP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ellOP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ellOP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ellOP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
% To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

\begin{figure}[t]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ellOP}$ (solid lines)
			%the property elicited by the ordered partition loss and embedded by $\LWW$, 
			juxtaposed against the level sets of $\mode$ (dashed lines).
%		The level sets of the mode (for which $\LWW$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ellOP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
      These offending cells correspond to reports whose highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

\subsection{Surrogates for top-$k$ classification}
\label{sec:top-k}
% In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
% Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
% Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.\raft{Not sure you can use ``observed'' like that (came up a few times)}
% The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
% \citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
% % for surrogate regret to approach target regret
% ~\citep{frongillo2021surrogate}.\jessiet{right?}
% \citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
% Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.
In settings like object recognition and information retrieval, it is natural to predict a set $S$ of labels.
In top-$k$ classification, one requires $|S|=k$, and given the true label $y$, the target loss is $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
In the literature on surrogates for top-$k$ classification, one goal has been to find a surrogate satisfying the following three desiderata: convexity, consistency, and piecewise linear (``hinge-like'') structure.
\citet{yang2018consistency} show that a number of previously proposed polyhedral losses, i.e., those which are convex and hinge-like, are inconsistent.
They further suggest that perhaps no surrogate could satisfy all three properties.
%\raft{Also, I cut the smooth vs hinge-like discussion since we don't really need the full motivation -- saying ``these weirdos wanted to do XYZ; who knows why'' is good enough, since our point is that our framework is useful for whatever people are trying to do \jessie{makes sense! \#burn}}

@@

\citet{finocchiaro2022consistenttopk} apply the general approach outlined above to each of the polyhedral surrogates shown to be inconsistent by \citeauthor{yang2018consistency}, and determine the target problems they do solve, i.e., the discrete losses they embed.
%\raft{Couldn't follow this sentence (commented out)}
% None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.  better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
%\jessiet{do we want to drop the table here or nah?}\raft{Yeah I'd say we should try it; it's at least helpful when discussing the constraints on the conditional label distributions, and besides, it's nice to have a figure for each section.  Sentence commented out below could be useful in the caption.}
% \citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf. $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing the algorithm to express varying levels of ``confidence'' on the top $k$ labels or report fewer than $k$ labels.
The label distributions for which these optimal reports differ from the optimal top-$k$ reports are shown in Table~\ref{tab:loss-slices} with $n=4$ and $k \in \{2,3\}$.
(Recall $n=|\Y|$, the number of labels.)

@@

For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK?}

Beyond analyzing the previously proposed surrogates, \citeauthor{finocchiaro2022consistenttopk} also use our framework to derive the first consistent polyhedral surrogate for $\elltopk$,
\begin{align}\label{eq:topk-embedding}
L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, n\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
\end{align}
That is, they show that a hinge-like surrogate does exist which is both convex and consistent.
In light of our framework, this fact is unsurprising: Theorems~\ref{thm:embed-poly-main} and~\ref{thm:link-main} imply that \emph{every} discrete loss has a consistent polyhedral surrogate.
This new surrogate $L^k$ is given directly by the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} and applying Theorem~\ref{thm:link-main} to obtain consistency.
While Theorem~\ref{thm:link-main} guarantees the existence of some consistent link function, the authors further ask whether the canonical argmax link function $\psi^k$, which returns the $k$ largest elements of $u$, is calibrated.
They indeed confirm its consistency using our framework, showing that $\psi^k$ is $\epsilon$-separated for $L^k$ and $\elltopk$, for any $\epsilon \leq \frac 1 {2n}$ \citep[Theorem 4.4]{finocchiaro2022consistenttopk}.
% confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
